---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

# **GLM.RMoE**: LASSO Regularized Mixture-of-Experts Models

<!-- badges: start -->
<!-- badges: end -->

`GLM.RMoE` is an R package for fitting regularized mixture-of-experts models with generalized linear experts. 

The package provides regularized Gaussian, multinomial, and Poisson mixture-of-experts models with LASSO-based feature selection.

The package accompanies the paper:

*Regularized Estimation and Feature Selection in Mixtures of Generalized Linear Experts.* Ref: arXiv:xxxx.xxxxx, September, 2026 by Thin Nguyen, Faicel Chamroukhi, Ha Hoang and Tuyen Huynh. Please cite the paper and the toolbox when using the code.

This package has three main functions:

| Function         | Model         |
| ---------------- | ------------- |
| `GaussRMoE()`    | Gaussian RMoE |
| `LogisticRMoE()` | Multinomial RMoE |
| `PoissonRMoE()`  | Poisson RMoE  |

# Installation

Install package:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("nv-thin/GLM-RMoE")
```

Install with vignettes:

```{r, eval = FALSE}
devtools::install_github(
  "nv-thin/GLM-RMoE",
  build_vignettes = TRUE,
  build_opts = c("--no-resave-data", "--no-manual")
)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("GLM.RMoE")
```

# Main features

- Gaussian regularized mixture-of-experts
- Multinomial regularized mixture-of-experts
- Poisson regularized mixture-of-experts
- LASSO-based feature selection
- Proximal Newton optimization
- Proximal Newton-type optimization

# Usage

```{r, message = FALSE}
library(GLM.RMoE)
```

<details>
  <summary>Gaussian Regularized Mixture-of-Experts</summary>

```{r, echo=TRUE}
# Application to a simulated data set

data("gaussian")
X <- as.matrix(gaussian[, -8])
y <- gaussian$V8

K <- 2 # Number of experts
Lambda <- 5
Gamma <- 5
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type

grmoe <- GaussRMoE(Xm = X, Ym = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)

grmoe$plot()
```

```{r, echo = TRUE}
# Application to a real data set

data("housing")
X <- as.matrix(housing[, -15])
y <- housing$V15

K <- 2 # Number of experts
Lambda <- 42
Gamma <- 10
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type

grmoe <- GaussRMoE(Xm = X, Ym = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)

grmoe$plot()
```

</details>

<details>
  <summary>Logistic Regularized Mixture-of-Experts</summary>

```{r, echo=TRUE}
# Application to a simulated data set

data("logistic")
X <- as.matrix(logistic[, -8])
y <- logistic$V8

K <- 2 # Number of experts
Lambda <- 3
Gamma <- 3
rho = 0.57
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type

lrmoe <- LogisticRMoE_L2(Xmat = X, Ymat = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)

lrmoe$plot()
```

```{r, echo = TRUE}
# Application to a real data set

data("ionosphere")
X <- as.matrix(ionosphere[, -35])
y <- ionosphere$V35

K <- 2 # Number of experts
Lambda <- 3
Gamma <- 3
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type

lrmoe <- LogisticRMoE(Xmat = X, Ymat = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)

lrmoe$plot()
```

</details>

<details>
  <summary>Poisson Regularized Mixture-of-Experts</summary>
  
```{r, echo=TRUE}
# Application to a simulated data set

data("poisson")
X <- as.matrix(poisson[, -8])
y <- poisson$V8

K <- 2 # Number of experts
Lambda <- 20
Gamma <- 10
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type

prmoe <- PoissonRMoE(Xmat = X, Ymat = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)

prmoe$plot()
```

```{r, echo = TRUE}
# Application to a real data set

data("cleveland")
X <- as.matrix(cleveland[, -15])
y <- cleveland$V15

K <- 2 # Number of experts
Lambda <- 10
Gamma <- 4
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type

prmoe <- PoissonRMoE(Xmat = X, Ymat = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)

prmoe$plot()
```

</details>
